---
title: "Conjoint Analysis for Product Development"
author: "Market Research Dept."
date: "30 Maret 2020"
subtitle: "Learning Forum"
institute: '@nutrifoodID'
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
    number_sections: yes
    theme: journal
    highlight: pygments
    fig_caption: yes
    code_folding: hide
    mathjax: local
    self_contained: yes
---


```{r setup, include=FALSE,warning=FALSE,message=FALSE}
rm(list=ls())
library(dplyr)
library(ggplot2)
load("bahan lefo.rda")
```

# __Apa itu Conjoint Analysis?__

> ___Conjoint analysis is a survey-based statistical technique used in market research that helps determine how people value different attributes (feature, function, benefits) that make up an individual product or service.___



# _Orthogonal_

```{r}
data.frame(x = c(-10:10),
           y = c(-10:10)) %>% 
  ggplot(aes(x = x,
             y = y)) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  theme_void()
```


# _Orthogonal_

## Aljabar Linear

> Apa sih _orthogonal_?

---

# _Factorial Design_

---

# _Factorial Design_


---

# _Case Study_

---

# _Case Study_

## Mie Instan

Suatu perusahaan hendak membuat mie instan varian terbaru. Beberapa alternatif pilihannya adalah:

1. Warna:
    1. Kuning
    1. Hijau
    1. Merah
1. Rasa:
    1. Soto
    1. Kari ayam
    1. Goreng jawa
1. Klaim:
    1. Less salt
    1. No msg
    1. Less fat

---

# _Factorial Design_

---

# _Factorial Design_

## Alternatif Mie Instan yang Ditanyakan ke Responden

```{r,warning=FALSE,message=FALSE}
factdesign %>% 
  rename(Warna = Var1,
         Rasa = Var2,
         Klaim = Var3) %>% 
  knitr::kable(caption = "Alternatif",align = "c")
```

---
# __Terima Kasih__
