---
title: "Conjoint Analysis for Product Development"
subtitle: "Learning Forum"
author: "Market Research Dept."
institute: "@nutrifoodID"
date: "30 Maret 2020"
output:
  xaringan::moon_reader:
    mathjax: default
    lib_dir: libs
    css: [default,"footer-header.css", fc, fc-fonts]
    seal: true
    nature:
      ratio: '18:10'
      slideNumberFormat: '%current%' 
      highlightStyle: ir-black
      highlightLines: true
      countIncrementalSlides: false
---
layout: true

<div class="my-footer"><span>Sebuah LeFo</span></div>
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE}
rm(list=ls())
library(dplyr)
library(ggplot2)
load("bahan lefo.rda")
```

class: center, middle, inverse
# __Apa itu Conjoint Analysis?__

---

class: center, middle
# _Conjoint Analysis_

## _Conjoint analysis_ is a survey-based statistical technique used in market research that helps determine how people value different attributes (feature, function, benefits) that make up an individual product or service.

---

class: center, middle, inverse
# _Orthogonal_

---

# _Orthogonal_

## Aljabar Linear

> Apa sih _orthogonal_?

---

class: center, middle, inverse
# _Factorial Design_

---

# _Factorial Design_


---

class: center, middle, inverse
# _Case Study_

---

# _Case Study_

## Mie Instan

Suatu perusahaan hendak membuat mie instan varian terbaru. Beberapa alternatif pilihannya adalah:

1. Warna:
    1. Kuning
    1. Hijau
    1. Merah
1. Rasa:
    1. Soto
    1. Kari ayam
    1. Goreng jawa
1. Klaim:
    1. Less salt
    1. No msg
    1. Less fat

---

class: center, middle, inverse
# _Factorial Design_

---

# _Factorial Design_

## Alternatif Mie Instan yang Ditanyakan ke Responden

```{r,echo=FALSE,warning=FALSE,message=FALSE}
factdesign %>% 
  rename(Warna = Var1,
         Rasa = Var2,
         Klaim = Var3) %>% 
  knitr::kable(caption = "Alternatif",align = "c")
```

---
class: center, middle, inverse
# __Terima Kasih__
